Modeling defoliation as a proxy for tree health: A case study using machine-learning and hyperspectral remote sensing data

### 2019-06-15 code/98-paper/journal/manuscript.tex
add manuscript.tex
upd bib
fix latex warnings, update bib

% arara: clean: { extensions: [aux, bcf, cod, blg, lof, lot, out, toc, xml, bak0 ] }

@@

% enable paragraph as 4th level https://tex.stackexchange.com/questions/60209/how-to-add-an-extra-level-of-sections-with-headings-below-subsubsection
\usepackage{titlesec}
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\small\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

@@

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{Above-Ground Biomass}
	\acro{ANN}{Artificial Neural Network}
	\acro{AUROC}{Area Under the Receiver Operating Characteristics Curve}
	\acro{BRT}{Boosted Regression Trees}
	\acro{CART}{Classification and Regression Trees}
	\acro{CV}{cross-validation}
	\acro{ENM}{Environmental Niche Modeling}
	\acro{FPR}{False Positive Rate}
	\acro{GAM}{Generalized Additive Model}
	\acro{GBM}{Gradient Boosting Machine}
	\acro{GLM}{Generalized Linear Model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{Interquartile Range}
	\acro{MARS}{Multivariate Adaptive Regression Splines}
	\acro{MEM}{Maximum Entropy Model}
	\acro{ML}{Machine-Learning}
	\acro{NDII}{Normalized Difference Infrared Index}
	\acro{NIR}{Near-Infrared}
	\acro{NRI}{Normalized Ratio Index}
	\acro{OLS}{Ordinary Least Squares}
	\acro{LOWESS}{Locally Weighted Scatter Plot Smoothing}
	\acro{PISR}{Potential Incoming Solar Radiation}
	\acro{RBF}{Radial Basis Function}
	\acro{RF}{Random Forest}
	\acro{RMSE}{Root Mean Square Error}
	\acro{RR}{Ridge Regression}
	\acro{RSS}{Residual Sum of Squares}
	\acro{SAR}{Synthetic Aperture Radar}
	\acro{SDM}{Species Distribution Modeling}
	\acro{SMBO}{Sequential-based Model Optimization}
	\acro{SVM}{Support Vector Machine}
	\acro{TPR}{True Positive Rate}
\end{acronym}

@@

@@

%\begin{figure} [t!]
%\begin{center}
%\makebox[\textwidth]{\includegraphics[width=\textwidth] {study_area_hyperspectral.pdf}}
%\caption{Information about the plot locations, the area of hyperspectral coverage and the number of trees per plot.}
%\label{fig:study_area}
%\end{center}
%\end{figure}

@@

\begin{itemize}
  \item Fitting times of the model increase
  \item Noise is possibly introduced into the model by highly-correlated variables \citep{johnstoneiainm2009}
  % I think we can phrase this better
  \item The interpretation and prediction of models containing hundreds of covariates becomes more complicated, up to to the point at which interpretation or prediction is not possible anymore \citep{johnstoneiainm2009}
\end{itemize}

@@

\noindent Relating the modeling error to plot characteristics (mean point density, coefficient of variation) did not show a clear picture: For both comparisons, \textit{Laukiz 2} did not follow the pattern that was observed from the other three plots (\autoref{fig:plot-characteristics}) of having an increase in error with an increase in mean point density and coefficient of variation.

It needs to be considered that we only looked at four plots in this work.
To make a robust statement about a possible relationship between modeling error and plot characteristics, a larger sample size of plots is needed.

@@

\noindent Other studies analyzing defoliation found that reflectance differences between defoliated and 30 \% defoliated trees of up to 10\% exist in the \ac{NIR} region \citep{rengara2016}.
This corresponds with the finding of this study that the most important variables are located in the NIR region.

>>>>

% arara: clean: { extensions: [bcf, cod, blg, lof, lot, out, toc, xml, bak0 ] }

@@

@@

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{Above-Ground Biomass}
	\acro{ANN}{Artificial Neural Network}
	\acro{AUROC}{Area Under the Receiver Operating Characteristics Curve}
	\acro{BRT}{Boosted Regression Trees}
	\acro{CART}{Classification and Regression Trees}
	\acro{CV}{cross-validation}
	\acro{ENM}{Environmental Niche Modeling}
	\acro{FPR}{False Positive Rate}
	\acro{GAM}{Generalized Additive Model}
	\acro{GBM}{Gradient Boosting Machine}
	\acro{GLM}{Generalized Linear Model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{Interquartile Range}
	\acro{MARS}{Multivariate Adaptive Regression Splines}
	\acro{MEM}{Maximum Entropy Model}
	\acro{ML}{Machine-Learning}
	\acro{NDII}{Normalized Difference Infrared Index}
	\acro{NIR}{Near-Infrared}
	\acro{NRI}{Normalized Ratio Index}
	\acro{OLS}{Ordinary Least Squares}
	\acro{LOWESS}{Locally Weighted Scatter Plot Smoothing}
	\acro{PISR}{Potential Incoming Solar Radiation}
	\acro{RBF}{Radial Basis Function}
	\acro{RF}{Random Forest}
	\acro{RMSE}{Root Mean Square Error}
	\acro{RR}{Ridge Regression}
	\acro{RSS}{Residual Sum of Squares}
	\acro{SAR}{Synthetic Aperture Radar}
	\acro{SDM}{Species Distribution Modeling}
	\acro{SMBO}{Sequential-based Model Optimization}
	\acro{SVM}{Support Vector Machine}
	\acro{TPR}{True Positive Rate}
	\acro{VI}{vegetation index}
	\acro{XGBOOST}{extreme gradient boosting}
\end{acronym}

@@

%\begin{figure} [t!]
%\begin{center}
%\makebox[\textwidth]{\includegraphics[width=\textwidth] {defoliation-distribution-plot.pdf}}
%\caption{Distribution of defoliation at trees for plots Laukiz 1, Laukiz 2, Luiando and Oiartzun.}
%\label{fig:defol-distr}
%\end{center}
%\end{figure}

@@

\begin{figure} [t!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[width=\textwidth] {study_area_hyperspectral.pdf}}
		\caption{Information about plot location and size, and spatial distribution of trees.}
		\label{fig:study_area}
	\end{center}
\end{figure}

@@

\begin{itemize}
	\item Fitting times of the model increase
	\item Noise is possibly introduced into the model by highly-correlated variables \citep{johnstoneiainm.2009}
	      % I think we can phrase this better
	\item The interpretation and prediction of models containing hundreds of covariates becomes more complicated, up to to the point at which interpretation or prediction is not possible anymore \citep{johnstoneiainm.2009}
\end{itemize}

@@

@@

\noindent Other studies analyzing defoliation found that reflectance differences between defoliated and 30 \% defoliated trees of up to 10\% exist in the \ac{NIR} region \citep{rengarajan2016}.
This corresponds with the finding of this study that the most important variables are located in the NIR region.
